Uncertainty Literature Review

### 2024-01-04 index.qmd
halfway through first draft of context section

@Otsuka2023 points out that the philosophy of statistics is build upon taking real world entities and boiling them down into probabilistic objects and this ontological process is largely dependent on our goals. For exmaple, when we record coin flips we typically want to model the behavior with a binomial distribution, so we ignore the outcome of a coin landing on its side despite the fact it is a real world possibility.

@Meng2014 shows that the entire concept of signal and noise are relative and the noise for one goal can be the signal for another. This break down is done by considering the data source, the "resolution" of the problem and data, and the phases involved in the analysis.

@Carlin2023

>>>>

@Otsuka2023 points out that the philosophy of statistics is build upon taking real world entities and boiling them down into probabilistic objects and this ontological process is largely dependent on our goals. For example, when we record coin flips we typically want to model the behavior with a binomial distribution, so we ignore the outcome of a coin landing on its side despite the fact it is a real world possibility.

@Meng2014 shows that the entire concept of signal and noise are relative and the noise for one goal can be the signal for another. This break down is done by considering the data source, the "resolution" of the problem and data, and the phases involved in the analysis. @Meng2021 highlights that data needs to be treated as an output from another process rahter than an value neutral input.

@Carlin2023 highlights a range of pitfalls that come up frequently when statisticians use regression models and they connect these pitfalls to the teaching of statistical methods as goal agnostic tools. @Carlin2023 suggest that every research question belongs to one of three distinct types: descriptive, predictive, and causal, each of which has its own appropriate statistical methods.

@Amar2005
